Nix for Polyglot, Reproducible Data Science Workflows

### 2025-10-23 paper.qmd
Add Python and Julia to keywords-formatted

keywords: [reproducibility, R, Nix]
keywords-formatted: [reproducibility, "[R]{.proglang}", "[Nix]{.pkg}"]
number-sections: true

>>>>

keywords: [reproducibility, R, Nix]
keywords-formatted: [reproducibility, "[R]{.proglang}", "[Python]{.proglang}", "[Julia]{.proglang}", "[Nix]{.pkg}"]
number-sections: true
